method

### 2022-01-26 06_Paper/ER-ED/method.Rmd
fixed issues in loop

>>>>

# import EMG data

datalist_EMG = lapply(list.files(here("04_RawData", "pilot", "ER-ED/EMG/analysis"), pattern = '*_Peaks.txt', full.names = TRUE),
                          read.table, stringsAsFactors = FALSE, header = TRUE)

# new empty frame to store files into
data_EMG = data.frame(ID = character(), segment = double(), Corr = double(), 
                     Lev = double())

# store EMG data in data_EMG frame
for (i in 1:length(datalist_EMG)) {

  tmp = data.frame(datalist_EMG[[i]][["Filename"]], 
                   datalist_EMG[[i]][["Segment"]], 
                   datalist_EMG[[i]][["T0T6000Corr.ASNM"]], 
                   datalist_EMG[[i]][["T0T6000Lev.ASNM"]])
  colnames(tmp) = names(data_EMG)

  data_EMG = rbind(tmp, data_EMG)

#rownames(data_ER) = 1:nrow(data_ER)
